Verifying Demonstrations

### 2018-11-29 paper/verifiability-analysis.tex
Replaces \paragraph with \subsubsection where necessary

\Cref{EligibilityVerif} states that anyone must be able to determine the authenticity of the relevant attributes of the data.
In \CROCUS, we have several attributes that must be verifiable: the time of 
creation (\ie, temporal eligibility, \cref{TemporallyRelated}), the physical 
location of \(\sk_P\) at creation (\ie, spatial eligibility, 
\cref{SpatiallyRelated}), recognition of two proofs originating from the same 
person (\ie, one-proof-per-person eligibility, \cref{CountOnce}) and that the 
proof is indeed designated for the event (\ie, designated-event eligibility, 
\cref{DesignatedEvent}).
It follows from \cref{analysis-individual} that the adversary cannot drop 
submitted proof shares and thus cannot decrease the count.
As indicated in \cref{in-system-adversary,deanonymizing-witness-adversary}, the 
adversary can submit proof shares as everyone else, so the adversary's only 
option is to increase the count.
We will thus let Alice pose as the adversary in this section, as she naturally 
has an incentive to increase the count.

>>>>

\Cref{EligibilityVerif} states that anyone must be able to determine the authenticity of the relevant attributes of the data.
In \CROCUS, we have several attributes that must be verifiable: the time of 
creation (\ie, temporal eligibility, \cref{TemporallyRelated}), the physical 
location of \(\sk_P\) at creation (\ie, spatial eligibility, 
\cref{SpatiallyRelated}), recognition of two proofs originating from the same 
person (\ie, one-proof-per-person eligibility, \cref{CountOnce}) and that the 
proof is indeed designated for the event (\ie, designated-event eligibility, 
\cref{DesignatedEvent}).
It follows from \cref{analysis-individual} that the adversary cannot drop 
submitted proof shares and thus cannot decrease the count.
As indicated in \cref{in-system-adversary,deanonymizing-storage-adversary}, the 
adversary can submit proof shares as everyone else, so the adversary's only 
option is to increase the count.
We will thus let Alice pose as the adversary in this section, as she naturally 
has an incentive to increase the count.
